%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNH}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}

\newcommand{\resumeProjectItem}[4]{%
  \noindent
  \textbf{#1 \href{#2}{[\underline{Link}]}} \hfill {#3} \\ % Project title + Link (left), Technologies (right)
  \vspace{-5pt} % Adjust the vertical spacing
  \begin{itemize} % Start itemized list for the description
    \item #4 % Description of the project
  \end{itemize}
  \vspace{-5pt} % Adjust overall spacing after the description
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListStartBullets}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Create resume header command. Parameters: name, email, phone, GitHub, location
\newcommand{\resumeHeader}[5]{
    \begin{center}
        {\Huge \textbf{#1}} \\[0.5em]
        \underline{\href{mailto:#2}{#2}} 
        \textbar \space #3 
        \textbar \space \underline{\href{https://github.com/#4}{github/#4}} 
        \textbar \space \underline{\href{https://linkedin.com/in/#5}{linkedin/#5}}
    \end{center}
}

\usepackage{array}
\makeatletter
\newcommand\HUGE{\@setfontsize\Huge{38}{47}} 
\newcolumntype{L}{>{\hb@xt@\z@\bgroup}l<{\hss\egroup}}
\newcolumntype{C}{>{\centering\arraybackslash}c}
\newcolumntype{R}{>{\hb@xt@\z@\bgroup\hss}r<{\egroup}}
\makeatother

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \resumeHeader{Shardul Negi}{shardul.exe@gmail.com}{+91-9660442629}{sharduln30}{shardulnegi}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manipal University}{Jaipur, India}
      {B.Tech in Computer Sc. \& Communication Engineering, CGPA: 8.75/10.0}{Aug 2016 -- Jun 2020}
      \resumeItemListStart
        \resumeItem{Coursework}
          {Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, Database Systems, Web Development}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {PayU}{Gurugram, India}
      {Senior Software Engineer \textbar{} Lending for \textbf{GPay, PhonePe, Paytm, Meesho, Swiggy, BharatPe}}{May 2022 -- Present}

      \resumeItemListStart
        \resumeItemNH{\textbf{Centralized Notification Service (CNS):} Architected unified notification platform replacing fragmented SMS \& Email infra, processing \textbf{10K--50K msgs/day}. Built retry engine with \textbf{DLQ}, reducing failures by \textbf{$\sim$40\%} and achieving \textbf{98\%+ delivery rate}. \textbf{Kafka} priority queues cut \textbf{OTP latency by $\sim$35\%}. Template engine reduced partner onboarding from \textbf{3--5 days to $<$2 hours}.}
        \resumeItemNH{\textbf{Partner Integration Platform:} Collaborated with \textbf{6 partner} engineering teams (\textbf{GPay, PhonePe, Paytm, Meesho, Swiggy, BharatPe}). Designed APIs for loan origination, disbursement \& mandates with \textbf{99.5\%+ uptime} and \textbf{sub-200ms p95} latency.}
        \resumeItemNH{\textbf{eNACH Mandate Integration:} Designed scalable eNACH mandate service achieving \textbf{$\sim$90\% success rate}. Integrated \textbf{Redis} caching \& \textbf{async processing}, boosting throughput by \textbf{3x}.}
        \resumeItemNH{\textbf{Loan Document Generation:} Template-based system using \textbf{Java Spring Boot} and \textbf{Thymeleaf} -- \textbf{60\%} less dev effort, \textbf{30\%} faster processing, near-zero document errors.}
        \resumeItemNH{\textbf{V-KYC Integration:} Delivered compliant \textbf{Video KYC} solution with intelligent method selection based on KYC type, improving compliance turnaround.}
      \resumeItemListEnd

    \resumeSubheading
      {Tata Consultancy Services}{Noida, India}
      {Software Engineer}{Oct 2020 -- May 2022}
      \resumeItemListStart
        \resumeItemNH{Built \textbf{microservice-based billing application} for accounting teams using \textbf{Spring Boot} and \textbf{MS SQL}, streamlining allowance processing workflows.}
        \resumeItemNH{Led \textbf{Oracle-to-Azure SQL data migration} using SSMA across \textbf{50+ tables} with \textbf{zero data loss}.}
        \resumeItemNH{Drove JUnit test coverage from \textbf{$\sim$30\% to 80\%+}, reducing production defects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}

    \resumeProjectItem{Online Doubt Support Portal}{https://online-doubt-support-portal.onrender.com}{HTML \textbar \space CSS \textbar \space JavaScript \textbar \space Bootstrap}{A portal integrated with whiteboard, code editor and chat box.
    \item Implemented chat box using Socket.IO, an event-based bidirectional communication layer for real-time web applications.}

    \resumeProjectItem{MS-Excel Clone}{https://github.com/sharduln30/Excel-Clone}{Web Application \textbar \space Data Structures}{A web application for basic tasks like saving, loading, and opening files, with text and cell editing features (font-size, font-style, text-align).
    \item Used graph theory to detect circular references while implementing the formula tab feature.
    \item Applied inbuilt stack functionality for Infix Evaluation in the formula tab. Implemented Topological Sort to resolve cell dependencies.}


%-----------LEADERSHIP & ACHIEVEMENTS-----------------
\section{Leadership \& Achievements}
  \resumeSubHeadingListStartBullets
    \resumeItemNH{\textbf{Architected PayU's CNS} from design doc to production -- backbone of all lending communication across \textbf{6 major partners} (GPay, PhonePe, Paytm, Meesho, Swiggy, BharatPe).}
    \resumeItemNH{Qualified for the \textbf{final round of INNOVRITI 4.0}, annual B-PLAN competition at Manipal University Jaipur (\textbf{top 5 of 100+ teams}).}
    \resumeItemNH{\textbf{Led cross-cultural team} as team head during Business Engineering program at \textbf{Heig-vd, Switzerland}.}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Java, SQL, HTML/CSS}
    \resumeSubItem{Frameworks \& Tools}
      {Spring Boot, Thymeleaf, Git, Redis, Kafka, Docker, Linux, AWS (S3, EC2, SES, SNS, SQS), CI/CD, JIRA}
    \resumeSubItem{Architecture}
      {Microservices, Event-Driven Architecture, REST APIs, System Design, Distributed Systems}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
